---
title: "tryout"
output: ioslides_presentation
date: "2025-05-11"
---

```{r setup, include=FALSE}
library(plotly)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r , echo = FALSE}
set.seed(123)
white_noise <- rnorm(100)
index <- 1:100
data <- data.frame(index = index, white_noise = white_noise)

fig <- plot_ly(data = data, 
               x = ~index, 
               y = ~white_noise, 
               type = 'scatter', 
               mode = 'lines+markers') %>%
  layout(title = "White Noise Time Series",
         xaxis = list(title = "Index"),
         yaxis = list(title = "Value"))

fig
```

